### 2019-08-21 maciek.tex
Costly rebalance
Omega(kl)

@@

>>>>

\section{Lower bound $\Omega(k\cdot \ell)$}

\maciek{Warning: sketch only, I did not finish writing it yet!}

In this section we assume the Online Clustering problem with the existence of a perfect partition of the input graph.

\begin{theorem}
  The competitive ratio of any deterministic algorithm for Online Clustering (with perfect partition) is $\Omega(k\cdot \ell)$.
\end{theorem}

\begin{proof}

@@

\section{Costly rebalance example $\Omega(k^2)$}
